### 2022-06-28 input/proposal.tex
reworked figure and 20p

\begin{table}
  \caption{\label{table:notations}Notation table.}
  \input{input/tablenotations.tex}
\end{table}

@@

\begin{proof}
Stale control information (see Definition~\ref{def:lwo}) may impair
the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} depicts a scenario comprising only three
\processes $a$, $b$, $c$ chained with FIFO links where \processes
receive the messages in the order of their sending. % ($s_{pq}(m)
%\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$).
In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. It echoes back $\alpha_c^3$ to $a$. In Figures~\ref{fig:problemD}
and \ref{fig:problemE}, $a$ and $b$ handle transiting
notifications. Finally, Figure~\ref{fig:problemF} shows that
eventually, $c$ stays in the deleted partition $P_a$ for not having
received $\delta_a$ that $b$ blocked earlier. The system does not
reach consistent partitioning. \end{proof}

>>>>

\begin{table}
  \caption{\label{table:notations}Summary of notations.}
  \input{input/tablenotations.tex}
\end{table}

@@

\begin{proof}
Stale control information (see Definition~\ref{def:lwo}) may impair
the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
In Figure~\ref{fig:problem}, $a$, $b$, $c$ are chained with FIFO links, \ie \processes
receive the messages in the order of their sending. % ($s_{pq}(m)
%\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$).
In Figure~\ref{fig:problemA}, $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB}, $a$ and $c$ delete their partition while
$b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. It echoes back $\alpha_c^3$ to $a$. In Figures~\ref{fig:problemD}
and \ref{fig:problemE}, $a$ and $b$ handle transiting
notifications. Finally, Figure~\ref{fig:problemF} shows that $c$ is stuck
in the deleted $P_a$ for not having received $\delta_a$ that
$b$ blocked earlier. The system does not reach consistent
partitioning. \end{proof}
